---
title: "crawler"
output: html_notebook
---


(Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*.)

First we want to make sure, we got all the packages we are going to use:
```{r}
install.packages(c('XML'))
```

Let's get started by crawling [StackOverflow's R question with the most votes](https://stackoverflow.com/questions/tagged/r?sort=votes&pageSize=50):

```{r}
library(httr)
library(XML)

# download website
url <- "https://stackoverflow.com/questions/tagged/r?sort=votes&pageSize=50"
response <- GET(url)

# parse HTML
doc <- htmlTreeParse(response, useInternalNodes = T)

# get all HTML elements with the "summarycount" class
countNodes <- getNodeSet(doc, "//div[contains(@class, 'summarycount')]")

# extract the value of the first element
countNode <- xmlValue(countNodes[[1]])

# print result!
cat('There are ', countNode, ' questions related to the R programming language!')
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
